Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.qmd
final small changes

We then added binary flags to differentiate between questions and answers. To do this in the first and second scripts, we separately re-parsed question and answer content using the XPath expressions `"chamber.xscript//question"` and `"chamber.xscript//answer"`, added the correct question and answer flags accordingly, and then added those flags back to the main dataframe based on exact text matches. For the third and fourth scripts, we made use of the fact that the patterns preceding text transcribed under a question node were stored separately from those transcribed under an answer node. As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to. Sometimes, **we identified** questions **which** were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags. For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer. **It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch. As such, users may identify and should be weary of occasional incorrectly flagged questions or answers in the data.**

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. **Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus on the user’s research does not require stage directions, then this can be removed by filtering observations in name equal to “business start”, or “stage direction”.**

>>>>

We then added binary flags to differentiate between questions and answers. To do this in the first and second scripts, we separately re-parsed question and answer content using the XPath expressions `"chamber.xscript//question"` and `"chamber.xscript//answer"`, added the correct question and answer flags accordingly, and then added those flags back to the main dataframe based on exact text matches. For the third and fourth scripts, we made use of the fact that the patterns preceding text transcribed under a question node were stored separately from those transcribed under an answer node. As a result, we could readily use those patterns to flag questions and answers correctly based on which list of patterns it belonged to. Sometimes, **we identified** questions **which** were incorrectly transcribed under an answer node and vice-versa, in which cases we manually corrected the question and answer flags. For instance, we check for any statements flagged as questions which include the phrase "has provided the following answer to the honourable member's question", in which case we re-code that statement as an answer. **It is important to note, however, that because we identified and corrected for these transcription errors manually as we discovered them, additional flagging errors may exist which we did not catch. As such, users may identify and should be wary of occasional incorrectly flagged questions or answers in the data.**

@@

When building our first scripts, one of the final components needed was to separate general stage directions out from statements made by MPs. Stage directions are general statements included in the transcript to document happenings in parliament. Examples of stage directions are "Bill read a second time", "Question agreed to", or "Debate adjourned". It was unclear to us from the XML and PDF who exactly these statements were attributed to. For further clarification, we watched portions of the video recording for some sitting days, and noticed that while these statements are documented in Hansard, they are not explicitly stated in parliament. For example, when the Deputy Speaker says "The question is that the bill be now read a second time", MPs vote, and if the majority is in favour, they proceed reading the bill the second time. This vote and second reading is not explicitly transcribed, rather what is written is: "Question agreed to. Bill read a second time". For this reason, we filled the name variable for these statements with "stage direction". Stage directions were not flagged as interjections. These stage directions are not defined differently from the regular debate speech in the XML, meaning we had to manually create a list of stage directions to separate out of the speeches. We built this list of stage directions as we worked backwards in parsing Hansard, and took the same approach across all four scripts. **Despite our best efforts to capture all stage directions in this list, because it had to be built manually, users should be aware that it is possible that some stage directions were not separated onto their own rows in the process. Further, it is important to note that because they are not spoken aloud, stage directions do not represent speech components in the same way that all other components such as interjections and continuations do. However, they provide valuable information about the inner-workings and structure of parliamentary events. If the focus of the user’s research does not require stage directions, then this can be removed by filtering observations in `name` equal to “business start”, or “stage direction”.**

### 2023-07-06 paper/paper-nature-revised.tex
final small changes

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[boxrule=0pt, sharp corners, interior hidden, borderline west={3pt}{0pt}{shadecolor}, frame hidden, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, \textbf{we identified} questions
\textbf{which} were incorrectly transcribed under an answer node and
vice-versa, in which cases we manually corrected the question and answer
flags. For instance, we check for any statements flagged as questions
which include the phrase ``has provided the following answer to the
honourable member's question'', in which case we re-code that statement
as an answer. \textbf{It is important to note, however, that because we
identified and corrected for these transcription errors manually as we
discovered them, additional flagging errors may exist which we did not
catch. As such, users may identify and should be weary of occasional
incorrectly flagged questions or answers in the data.}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events. If the focus on the user's research does not require stage
directions, then this can be removed by filtering observations in name
equal to ``business start'', or ``stage direction''.}

>>>>

\begin{document}
\maketitle
\begin{abstract}
Public knowledge of what is said in parliament is a tenet of democracy,
and a critical resource for political science research. In Australia,
following the British tradition, the written record of what is said in
parliament is known as Hansard. While the Australian Hansard has always
been publicly available, it has been difficult to use for the purpose of
large-scale macro- and micro-level text analysis because it has only
been available as PDFs or XMLs. Following the lead of the Linked
Parliamentary Data project which achieved this for Canada, we provide a
new, comprehensive, high-quality, rectangular database that captures
proceedings of the Australian parliamentary debates from 1998 to 2022.
The database is publicly available and can be linked to other datasets
such as election results. The creation and accessibility of this
database enables the exploration of new questions and serves as a
valuable resource for both researchers and policymakers.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, boxrule=0pt, enhanced, interior hidden, breakable, sharp corners, frame hidden]}{\end{tcolorbox}}\fi

@@

We then added binary flags to differentiate between questions and
answers. To do this in the first and second scripts, we separately
re-parsed question and answer content using the XPath expressions
\texttt{"chamber.xscript//question"} and
\texttt{"chamber.xscript//answer"}, added the correct question and
answer flags accordingly, and then added those flags back to the main
dataframe based on exact text matches. For the third and fourth scripts,
we made use of the fact that the patterns preceding text transcribed
under a question node were stored separately from those transcribed
under an answer node. As a result, we could readily use those patterns
to flag questions and answers correctly based on which list of patterns
it belonged to. Sometimes, \textbf{we identified} questions
\textbf{which} were incorrectly transcribed under an answer node and
vice-versa, in which cases we manually corrected the question and answer
flags. For instance, we check for any statements flagged as questions
which include the phrase ``has provided the following answer to the
honourable member's question'', in which case we re-code that statement
as an answer. \textbf{It is important to note, however, that because we
identified and corrected for these transcription errors manually as we
discovered them, additional flagging errors may exist which we did not
catch. As such, users may identify and should be wary of occasional
incorrectly flagged questions or answers in the data.}

@@

When building our first scripts, one of the final components needed was
to separate general stage directions out from statements made by MPs.
Stage directions are general statements included in the transcript to
document happenings in parliament. Examples of stage directions are
``Bill read a second time'', ``Question agreed to'', or ``Debate
adjourned''. It was unclear to us from the XML and PDF who exactly these
statements were attributed to. For further clarification, we watched
portions of the video recording for some sitting days, and noticed that
while these statements are documented in Hansard, they are not
explicitly stated in parliament. For example, when the Deputy Speaker
says ``The question is that the bill be now read a second time'', MPs
vote, and if the majority is in favour, they proceed reading the bill
the second time. This vote and second reading is not explicitly
transcribed, rather what is written is: ``Question agreed to. Bill read
a second time''. For this reason, we filled the name variable for these
statements with ``stage direction''. Stage directions were not flagged
as interjections. These stage directions are not defined differently
from the regular debate speech in the XML, meaning we had to manually
create a list of stage directions to separate out of the speeches. We
built this list of stage directions as we worked backwards in parsing
Hansard, and took the same approach across all four scripts.
\textbf{Despite our best efforts to capture all stage directions in this
list, because it had to be built manually, users should be aware that it
is possible that some stage directions were not separated onto their own
rows in the process. Further, it is important to note that because they
are not spoken aloud, stage directions do not represent speech
components in the same way that all other components such as
interjections and continuations do. However, they provide valuable
information about the inner-workings and structure of parliamentary
events. If the focus of the user's research does not require stage
directions, then this can be removed by filtering observations in
\texttt{name} equal to ``business start'', or ``stage direction''.}
